cardinalR: Generating interesting high-dimensional data structures

### 2025-05-01 paper-cardinalR.Rmd
Added initial sphere projections

>>>>

```{r data-circle, echo=TRUE}
circle <- gen_circle(n = 1000, p = 4)
```

```{r, eval=FALSE}
langevitour::langevitour(circle)
```

```{r circle-proj1}
scaled_data <- scale_data_manual(circle)

circle_proj1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.65, 0.7), 
  title = "a1", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r circle-proj2}

circle_proj2 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.7, 0.6), 
  title = "a2", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r circle-proj3}

circle_proj3 <- plot_proj(
  proj_obj = proj_obj3, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.5, 0.62), 
  title = "a3", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r, label = "fig-circle-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `circle` data."}
#| fig-width: 15
#| fig-height: 5

circle_proj1 + circle_proj2 + circle_proj3 +
  plot_layout(ncol = 3, guides = "collect") 
```

```{r data-curvycycle, echo=TRUE}
curvycycle <- gen_curvycycle(n = 1000, p = 4)
```

```{r, eval=FALSE}
langevitour::langevitour(curvycycle)
```

```{r curvycycle-proj1}
scaled_data <- scale_data_manual(curvycycle)

curvycycle_proj1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.65, 0.7), 
  title = "a1", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r curvycycle-proj2}

curvycycle_proj2 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.7, 0.6), 
  title = "a2", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r curvycycle-proj3}

curvycycle_proj3 <- plot_proj(
  proj_obj = proj_obj3, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.5, 0.62), 
  title = "a3", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r, label = "fig-curvycycle-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `curvycycle` data."}
#| fig-width: 15
#| fig-height: 5

curvycycle_proj1 + curvycycle_proj2 + curvycycle_proj3 +
  plot_layout(ncol = 3, guides = "collect") 
```

```{r data-unifsphere, echo=TRUE}
unifsphere <- gen_unifsphere(n = 1000, p = 4)
```

```{r, eval=FALSE}
langevitour::langevitour(unifsphere)
```

```{r unifsphere-proj1}
scaled_data <- scale_data_manual(unifsphere)

unifsphere_proj1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.65, 0.7), 
  title = "a1", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r unifsphere-proj2}

unifsphere_proj2 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.7, 0.6), 
  title = "a2", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r unifsphere-proj3}

unifsphere_proj3 <- plot_proj(
  proj_obj = proj_obj3, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.5, 0.62), 
  title = "a3", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r, label = "fig-unifsphere-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `unifsphere` data."}
#| fig-width: 15
#| fig-height: 5

unifsphere_proj1 + unifsphere_proj2 + unifsphere_proj3 +
  plot_layout(ncol = 3, guides = "collect") 
```

```{r data-gridedsphere, echo=TRUE}
gridedsphere <- gen_gridedsphere(n = 1000, p = 4)
```

```{r, eval=FALSE}
langevitour::langevitour(gridedsphere)
```

```{r gridedsphere-proj1}
scaled_data <- scale_data_manual(gridedsphere)

gridedsphere_proj1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.65, 0.7), 
  title = "a1", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r gridedsphere-proj2}

gridedsphere_proj2 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.7, 0.6), 
  title = "a2", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r gridedsphere-proj3}

gridedsphere_proj3 <- plot_proj(
  proj_obj = proj_obj3, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.5, 0.62), 
  title = "a3", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r, label = "fig-gridedsphere-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `gridedsphere` data."}
#| fig-width: 15
#| fig-height: 5

gridedsphere_proj1 + gridedsphere_proj2 + gridedsphere_proj3 +
  plot_layout(ncol = 3, guides = "collect") 
```

```{r data-clusteredspheres, echo=TRUE}
clusteredspheres <- gen_clusteredspheres(n = c(1000, 100), k = 3, p = 4, r = c(15, 3),
                                         loc = 10 / sqrt(3)) |>
  dplyr::select(-cluster)
```

```{r, eval=FALSE}
langevitour::langevitour(clusteredspheres)
```

```{r clusteredspheres-proj1}
scaled_data <- scale_data_manual(clusteredspheres)

clusteredspheres_proj1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.65, 0.7), 
  title = "a1", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r clusteredspheres-proj2}

clusteredspheres_proj2 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.7, 0.6), 
  title = "a2", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r clusteredspheres-proj3}

clusteredspheres_proj3 <- plot_proj(
  proj_obj = proj_obj3, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.5, 0.62), 
  title = "a3", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r, label = "fig-clusteredspheres-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `clusteredspheres` data."}
#| fig-width: 15
#| fig-height: 5

clusteredspheres_proj1 + clusteredspheres_proj2 + clusteredspheres_proj3 +
  plot_layout(ncol = 3, guides = "collect") 
```

```{r data-hemisphere, echo=TRUE}
hemisphere <- gen_hemisphere(n = 1000, p = 4)
```

```{r, eval=FALSE}
langevitour::langevitour(hemisphere)
```

```{r hemisphere-proj1}
scaled_data <- scale_data_manual(hemisphere)

hemisphere_proj1 <- plot_proj(
  proj_obj = proj_obj1, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.65, 0.7), 
  title = "a1", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r hemisphere-proj2}

hemisphere_proj2 <- plot_proj(
  proj_obj = proj_obj2, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.7, 0.6), 
  title = "a2", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r hemisphere-proj3}

hemisphere_proj3 <- plot_proj(
  proj_obj = proj_obj3, 
  point_param = c(1.5, 0.2, "#000000"), # size, alpha, color
  plot_limits = c(-0.5, 0.62), 
  title = "a3", 
  cex = 2, 
  axis_text_size = 5,
  is_color = FALSE)

```{r, label = "fig-hemisphere-proj", fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `hemisphere` data."}
#| fig-width: 15
#| fig-height: 5

hemisphere_proj1 + hemisphere_proj2 + hemisphere_proj3 +
  plot_layout(ncol = 3, guides = "collect") 
```
